Insight Into Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-09-01 draft.tex
Revised abstract

% \abstract{
% The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size. Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
\abstract{ 
% Motivation
Epidemiology is the study of causation of diseases.
%%
Subject groups (a cohort) is analyzed to correlate lifestyle and medical variables with diseases.
%%
Most recently, large cohort studies also acquire medical image data.
%% Problem statement
We correlate image-derived variables from the lumbar spine with lower back pain.
%% Approach
Our analysis is based on detection masks from a semi-automatic model based detection of 2,540 lumbar spines.
%%
From the detection masks, we derive shape-describing variables, such as course, curvature and torsion of the spine canal.
%%
We classify non-image parameter using decision trees created using the C4.5/C5.0 algorithm.
%%
The analysis yields a decision tree per non-image parameter.
%%
We make these trees comparable by introducing tree size and a classification error rate metrics.
%%
A interactive scatterplot visualization allows to compare the decision trees.
%%
%\\\\
% Results
% Conclusions
We conclude that the metrics extracted from the detection masks are only sufficient for classification of lifestyle factors, such as gender or nutrition.
%%
The presented approach is a valuable extension to the interactive visual analysis of epidemiological data and not limited to image-parameter analysis.
}

>>>>

% \abstract{
% The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size. Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
\abstract{ 
% Motivation
Epidemiology is the study of causation of diseases.
%%
Subject groups (a cohort) are analyzed to correlate lifestyle and medical properties with diseases.
%%
Most recently, large cohort studies also acquire medical image data.
%% Problem statement
%%
We want to assess the predictive quality of image-derived variables for lower back pain
%%
%We correlate image-derived variables from the lumbar spine with lower back pain.
%% Approach
Our analysis is based on masks from a semi-automatic model based detection of 2,540 lumbar spines.
%%
These masks are quantified using shape-describing variables, such as spine canal course, -curvature and -torsion.
%From the detection masks, we derive shape-describing variables, such as course, curvature and torsion of the spine canal.
%%
Using the C4.5/C5.0 algorithm we created decision trees to predict non-image parameter, such as pain indicators or occupational circumstances.
%We classify non-image parameter using decision trees created using the C4.5/C5.0 algorithm.
%%
The analysis yields a decision tree per non-image parameter.
%%
%We make these trees comparable in a scatter plot using the \emph{tree size} and a \emph{classification error rate} metric.
We make these trees comparable by using the \emph{tree size} and a \emph{classification error rate} metric.
%%
A interactive scatterplot visualization allows to compare the decision trees.
%%
The comparative analysis was performed on subjects divided by age, gender and body size to assess the influences of these variables.
%%
%\\\\
% Results
% Conclusions
We conclude that the metrics extracted from the detection masks are only sufficient for classification of lifestyle factors, such as gender or nutrition.
%%
The presented approach is a valuable extension to the interactive visual analysis of epidemiological data and is not limited to image-parameter analysis.
}
